---
title: "Exploration"
author: "Tommy Lang"
date: "7/3/2018"
output:
  html_notebook:
    code_folding: hide
    df_print: paged
    fig_height: 4
    fig_width: 7
    highlight: tango
    number_sections: yes
    theme: readable
    toc: yes
    toc_float: yes
---

# Packages, Data and Custom Functions

Custom Functions:
This code chunk contains custom fucntions that I use to help automate or make
tasks easier.
```{r message=FALSE}
LoadPackages <- function(packages) {
  # Load or install packages if they aren't already loaded.
  #
  # Args:
  #   packages: a vector of package names
  #
  for (package in packages) {
    if (!require(package, character.only=T, quietly=T)) {
      if (!package %in% installed.packages()) install.packages(package)
      library(package, character.only=T)
    }
  }
}

ColNa <- function(df) {
  # Return a vector of column names that have NA values
  #
  # Args:
  # df: data frame 
  #
  # Returns:
  #  vector of column names that have NAs 
  df <- tbl_df(df)
  v <- c()
  j <- 1
  for(i in 1:ncol(df)) {
    x <- df[ ,i]
    xRmvNA <- x[!is.na(x),]
    lenx <- nrow(x)
    lenxRmvNA <- nrow(xRmvNA)
    if(lenx != lenxRmvNA ) {
      v[j] <- colnames(df[ ,i])
      j <- j+1
    }
  }
  return(v)
}

ReplaceNonNum <- function(x) {
  str_replace_all(x, "[^.0-9]+", "")
}

data <- 'C:/Users/tlang/Documents/GitHub/Summer_Practicum_19_blue_9/Data/'
```

Load Packages:
Packages contain functions that others write that help with doing stuff
```{r, results=FALSE}
# I use my custom function LoadPackages to load or install packages
LoadPackages(c("dplyr", "haven", "stringr", "tidyr", 
               "ggplot2", "missForest", "caret",
               "Boruta"))
```


Read in data
```{r results = FALSE}
data_path <- 'E:/Tommy/Original_Data/Data'
# The list.files function gets the file names in a specified directory
# file_names contains the file names of all the data sets
file_names <- list.files(path = data_path, recursive = TRUE)

# Initialize a vector to hold data frame names
df_names <- c()
i <- 1

# This loop goes through the file names and reads it into R
for(name in file_names) {
  # create variable name for df
  df_name <- str_replace_all(name, " |_with_ann2|.sas7bdat|/acs_16_5yr|_records", "")
  # read in data
  df <- read_sas(paste0(data_path, "/", name))
  df <- df %>% mutate_all(funs(as.character(.)))
  # attach df to variable name
  assign(df_name, df) 
  print(paste0("done with: ", df_name, " ", i,"/",length(file_names)))
  i <- i+1
  # add the current iteration of the data frame name to the df_names vector
  df_names <- c(df_names, df_name)
}
```

city, Zip, Specialty, Product_Group makes a unique id
```{r}
# rx_trx %>% dplyr::group_by(city, Zip, Specialty, Product_Group) %>%
#   mutate(rn = row_number()) %>% 
#   arrange(city, Zip, Specialty, Product_Group, rn) %>% 
#   filter(rn > 1) %>%
#   select(city, Zip, Specialty, Product_Group, PG_Name, rn)
```

```{r}
race <- bind_rows(MA_b02001, NC_b02001, OR_b02001)
age_sex <- bind_rows(MA_s0101, NC_s0101, OR_s0101)
house_fam <- bind_rows(MA_s1101, NC_s1101, OR_s1101)
martial <- bind_rows(MA_s1201, NC_s1201, OR_s1201)
school_enroll <- bind_rows(MA_s1401, NC_s1401, OR_s1401)
education_attainment <- bind_rows(MA_s1501, NC_s1501, OR_s1501)
poverty <- bind_rows(MA_s1701, NC_s1701, OR_s1701)
income <- bind_rows(MA_s1901, NC_s1901, OR_s1901)
employment <- bind_rows(MA_s2301, NC_s2301, OR_s2301)
```


```{r}
# Race Dataset _______________________________________________
race_k <- race %>% select(1:9)

# these are all totals
names(race_k) <- c("Zip", 
                   "tot_pop", 
                   "white", 
                   "black", 
                   "native", 
                   "asian", 
                   "hawaiian", 
                   "other", 
                   "two_more")

# Age/ Sex data set ___________________________________________

# age_sex_k <- age_sex %>%
#   select(Zip, HC01_EST_VC01, HC02_EST_VC01, HC03_EST_VC01,
#          HC01_EST_VC35, HC02_EST_VC35, HC03_EST_VC35,
#          HC01_EST_VC37,  HC01_EST_VC38,  HC01_EST_VC39)
# 
# names(age_sex_k) <- c("Zip",
#                       "tot_pop",
#                       "male_pop",
#                       "female_pop",
#                       "median_age",
#                       "m_median_age",
#                       "f_median_age",
#                       "age_depen_ratio",
#                       "old_depen_ratio",
#                       "child_depen_ratio")

# These are all percentages besides and median age                
age_sex_k <- age_sex %>% 
  select(-HC01_EST_VC01, -HC02_EST_VC01, -HC03_EST_VC01, 
         -ends_with("VC42"), -ends_with("VC43"))
  
names(age_sex_k) <- paste0(names(age_sex_k), "_age_sex")
names(age_sex_k)[1] <- "Zip"
  

# Household and families data set ________________________________

house_fam_k <- house_fam %>% 
  select("Zip", 2:7, 12:17,
         HC01_EST_VC27,
         HC01_EST_VC28,
         HC01_EST_VC29,
         HC01_EST_VC32,
         HC01_EST_VC33)

names(house_fam_k) <- c("Zip", 
                        'tot_households', 
                        'tot_households_married',
                        'tot_households_male', 
                        'tot_households_female',
                        'tot_households_nfamily',
                        'avg_household_size',
                        'tot_fam',
                        'tot_fam_married',
                        'tot_fam_male',
                        'tot_fam_female',
                        'tot_fam_nfamily',
                        'avg_fam_size',
                        "unit1_p",
                        "unit2_p",
                        "other_type_unit_p",
                        "tot_owner_units_p",
                        "tot_renter_units_p")

# Martial data set ____________________________________________________________
# These are all percentages
martial_k <- martial %>% 
  select(Zip, starts_with("HC02"), starts_with("HC03"), starts_with("HC04"),
         starts_with("HC05"), starts_with("HC06")) %>%
  select(-ends_with("VC39"))

names(martial_k) <- paste0(names(martial_k), "_martial")
names(martial_k)[1] <- "Zip"

# names(martial_k) <- c("Zip",
#                       "tot_pop_over_15",
#                       "now_married_per",
#                       "widowed_per",
#                       "divorced_per",
#                       "separated_per",
#                       "never_married_per")


# school enrollment____________________________________________________________
# all percentages
school_enroll_k <- school_enroll %>% 
  select(Zip, starts_with("HC02"), starts_with("HC04"),
         starts_with("HC06"))

names(school_enroll_k) <- paste0(names(school_enroll_k), "_enroll")
names(school_enroll_k)[1] <- "Zip"

# Education attainment____________________________________________________________
# all percentages
education_attainment_k <- education_attainment %>% 
  select(Zip, starts_with("HC02"), starts_with("HC04"),
         starts_with("HC06"))

names(education_attainment_k) <- paste0(names(education_attainment_k), "_edu")
names(education_attainment_k)[1] <- "Zip"

# Proverty____________________________________________________________
#all percentages
poverty_k <- poverty %>% 
  select(Zip, starts_with("HC03"))

names(poverty_k) <- paste0(names(poverty_k), "_poverty")
names(poverty_k)[1] <- "Zip"

# Income___________________________________________________________________________
# needs to be changed into percentages? or it looks like it already is
# All perentages or mean median income
income_k <- income %>%
  select(-ends_with("VC18"), -ends_with("VC19"), -ends_with("VC20"), -ends_with("VC01"))

names(income_k) <- paste0(names(income_k), "_income")
names(income_k)[1] <- "Zip"

# Employment___________________________________________________________________________
# all percentages
employment_k <- employment %>%
  select(Zip, starts_with('HC02'), starts_with('HC03'),starts_with('HC04'))

names(employment_k) <- paste0(names(employment_k), "_empl")
names(employment_k)[1] <- "Zip"
```

Join the data sets
```{r}
joined_dem <- race_k %>% 
  inner_join(age_sex_k, "Zip") %>%
  inner_join(house_fam_k, "Zip") %>%
  inner_join(martial_k,"Zip") %>%
  inner_join(school_enroll_k, "Zip") %>%
  inner_join(education_attainment_k, "Zip") %>%
  inner_join(poverty_k, "Zip") %>%
  inner_join(income_k, "Zip") %>%
  inner_join(employment_k, "Zip")
```

Replace non numeric with empty string and cast to double
```{r}
dem_c <- joined_dem %>% 
  mutate_at(2:ncol(joined_dem), funs(ReplaceNonNum(.))) 

dem_c[dem_c == ""] <- NA

dem_c <- dem_c %>% 
  mutate_at(2:ncol(dem_c), funs(as.double(.))) 
```

Check missing values
```{r}
# col_names <- names(joined_dem)
# 
# missing_values <- c()
# foo <- c()
# 
# for(name in col_names) {
#   mis_zip <- dem_c %>% 
#     filter(is.na(get(name))) %>% pull(Zip)
#   
#   org_missing <- joined_dem %>% filter(Zip %in% as.character(mis_zip))
#   foo <- org_missing %>% pull(get(name))
#   missing_values <- c(missing_values, foo)
# }
# 
# table(missing_values)
```

```{r}
dem_c <- dem_c %>% 
  mutate(white_p = white / tot_pop,
         black_p = black / tot_pop,
         native_p = native / tot_pop,
         asian_p = asian / tot_pop,
         hawaiian_p = hawaiian / tot_pop,
         other_p = other / tot_pop,
         two_more_p = two_more / tot_pop,
         tot_households_p = tot_households / tot_pop,
         tot_households_married_p = tot_households_married / tot_pop,
         tot_households_male_p = tot_households_male / tot_pop,
         tot_households_female_p = tot_households_female / tot_pop,
         tot_households_nfamily_p = tot_households_nfamily / tot_pop,
         tot_fam_p = tot_fam / tot_pop,
         tot_fam_married_p = tot_fam_married / tot_pop,
         tot_fam_male_p = tot_fam_male / tot_pop,
         tot_fam_female_p = tot_fam_female / tot_pop,
         tot_fam_nfamily_p = tot_fam_nfamily / tot_pop
         ) %>%
  select(-white,
         -black,
         -native,
         -asian,
         -hawaiian,
         -other, 
         -two_more,
         -tot_households,
         -tot_households_married,
         -tot_households_male,
         -tot_households_female,
         -tot_households_nfamily,
         -tot_fam,
         -tot_fam_married,
         -tot_fam_male,
         -tot_fam_female,
         -tot_fam_nfamily)

```

Create state features
```{r}
MA <- MA_b02001 %>% select(Zip) %>% mutate(state = 'MA')
NC <- NC_b02001 %>% select(Zip) %>% mutate(state = 'NC')
OR <- OR_b02001 %>% select(Zip) %>% mutate(state = 'OR')
state <- bind_rows(MA, NC, OR)

dem_c <- dem_c %>% inner_join(state, 'Zip') %>%
  mutate_at("state", funs(as.factor))

saveRDS(dem_c, paste0(data,"dem_c.rds"))
```


Keep features that are less than 5% missing
```{r}
all_obs <- rx_trx %>% 
  distinct(Zip) %>% 
  inner_join(dem_c, "Zip")

all_na_cols <- colSums(is.na(all_obs)) %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() 

d_na_cols <- all_na_cols %>% filter(. > .05*nrow(all_obs)) %>% pull(rowname)
all_cols <- names(all_obs)
keep_cols <- setdiff(all_cols, d_na_cols)

features <- dem_c %>% select(keep_cols)
```

Split into train and test sets
```{r}
set.seed(888)
train_p <- features %>% sample_frac(.8)
test_p  <- anti_join(features, train_p, by = 'Zip')
```

Impute missing values for train set
```{r}
train_imp <- train_p %>% select(-Zip)
train_imp <- as.data.frame(train_imp)

set.seed(8)
train_imp2 <- missForest(train_imp, verbose = TRUE)

train_impd <- bind_cols(train_p %>% select(Zip), train_imp2$ximp)

saveRDS(train_imp2, paste0(data,'train_impd.rds'))
# train_impd <- readRDS(paste0(data,'train_impd.rds'))
```


Imput missing values for test set
```{r}
test_imp <- test_p %>% select(-Zip)
test_imp <- as.data.frame(test_imp)

set.seed(8)
test_imp2 <- missForest(test_imp, verbose = TRUE)

test_impd <- bind_cols(test_p %>% select(Zip), test_imp2$ximp)

saveRDS(test_imp2, paste0(data,'test_impd.rds'))
```

Response Variables
```{r}
pop <- dem_c %>% 
  select(Zip, tot_pop)
city <- rx_trx %>% 
  distinct(Zip, city, ST)

end <- which(names(rx_trx) == "TRx_09302015")
beg <- which(names(rx_trx) == "TRx_08312017")
rx_trx <- rx_trx %>% mutate_at(beg:end, funs(as.double(.)))

rx_trx$total <- rowSums(rx_trx[ ,beg:end] )

tot_rx <- rx_trx %>% 
  group_by(Zip) %>% 
  summarise(t_rx = sum(total),
            t_rx_end = sum(TRx_08312017)) %>%
  ungroup()

# Normalize totals
#1245 in rx but only 1189 matches in dem data with 2 zero
# drop obs where tot_pop is zero because can't mix zip codes
rx_p <- tot_rx %>% 
  left_join(pop, "Zip") %>%
  mutate(tot_pop = ifelse(tot_pop == 0, NA, tot_pop)) %>%
  filter(!is.na(tot_pop)) %>%
  mutate(t_rx_p = round((t_rx / tot_pop) *1000,2),
         t_rx_end_p = round((t_rx_end / tot_pop) * 1000,2)) %>%
  select(-t_rx, -t_rx_end, -tot_pop)

p_20 <- quantile(rx_p$t_rx_p , probs = 0.80) %>% unname()

resp_v1 <- rx_p %>%
  mutate(rx_p_high = ifelse(t_rx_p > p_20, "pos", "neg")) %>%
  mutate_at('rx_p_high', funs(as.factor(.)))
```

# Regression

```{r}
train_v1 <- resp_v1 %>% 
  select(Zip, t_rx_p) %>% 
  inner_join(train_impd, "Zip")

train_v1_zip <- train_v1 %>% 
  select(Zip)

train_v1 <- train_v1 %>%
  select(-Zip)
```

```{r}
test_v1 <- resp_v1 %>% 
  select(Zip, t_rx_p) %>% 
  inner_join(test_impd, "Zip")

test_v1_zip <- test_v1 %>% 
  select(Zip)

test_v1 <- test_v1 %>%
  select(-Zip)
```


Boruta
```{r}
set.seed(888)
boruta_train <- Boruta(t_rx_p ~., data = train_v1, doTrace = 2, maxRuns = 88)

final_boruta <- TentativeRoughFix(boruta_train)

boruta_df <- attStats(final_boruta) %>% 
  tibble::rownames_to_column() %>% arrange(desc(meanImp))

imp_p <- getSelectedAttributes(final_boruta, withTentative = T)

saveRDS(final_boruta, paste0(data,"final_boruta.rds"))
write.csv(boruta_df, paste0(data, "boruta_df.csv"))
```

```{r}
train_v1_imp <- train_v1[c('t_rx_p', imp_p)]

ctrl_r <- trainControl(method = "repeatedcv", 
                       number = 10, 
                       repeats = 1,
                       verboseIter = TRUE)

set.seed(88)
rf_v1 <- train(t_rx_p ~., data = train_v1_imp, method = "ranger")

rf_v1


```

try rf with all predictors
```{r}
rf_all <- train(t_rx_p ~., data = train_v1, method = "ranger")

rf_all
```


# Classification  

```{r}
train_v2 <- resp_v1 %>% 
  select(Zip, rx_p_high) %>% 
  inner_join(train_impd, "Zip")

train_v2_zip <- train_v2 %>% 
  select(Zip)

train_v2 <- train_v2 %>%
  select(-Zip)
```

```{r}
test_v2 <- resp_v1 %>% 
  select(Zip, rx_p_high) %>% 
  inner_join(test_impd, "Zip")

test_v2_zip <- test_v2 %>% 
  select(Zip)

test_v2 <- test_v2 %>%
  select(-Zip)
```


Boruta
```{r}
set.seed(888)
boruta_train_c <- Boruta(rx_p_high ~., data = train_v2, doTrace = 2, maxRuns = 88)

final_boruta_c <- TentativeRoughFix(boruta_train_c)

boruta_df_c <- attStats(final_boruta_c) %>% 
  tibble::rownames_to_column() %>% arrange(desc(meanImp))

imp_p_c <- getSelectedAttributes(final_boruta_c, withTentative = T)

saveRDS(final_boruta_c, paste0(data,"final_boruta_c.rds"))
write.csv(boruta_df_c, paste0(data, "boruta_df_c.csv"))
```



```{r}
train_v2_imp <- train_v2[c('rx_p_high', 
                           "tot_households_nfamily_p", 
                           "avg_household_size",
                           "unit2_p",
                           "tot_renter_units_p",
                           
                           "HC03_EST_VC20_age_sex",
                           "tot_households_p",
                           "HC02_EST_VC21_martial",
                           "tot_households_married_p",
                           "HC02_EST_VC30_edu",
                           "HC03_EST_VC33_poverty") ]

ctrl_c <- trainControl(method = "repeatedcv", 
                       number = 10, 
                       repeats = 1,
                       verboseIter = TRUE)
set.seed(88)
rf_c <- train(rx_p_high ~., data = train_v2_imp, method = "ranger")

rf_c

set.seed(88)
glm_c <- train(rx_p_high ~., data = train_v2_imp, method = "glm")

glm_c

foo <-glm(rx_p_high ~., data = train_v2_imp, family = binomial)


```

test set performance
```{r}
confusionMatrix(predict(glm_c, test_v2), test_v2$rx_p_high)
```


```{r}
str(foo)

data.frame(foo$coefficients) %>% 
  tibble::rownames_to_column() %>% 
  spread(key = rowname, value = foo.coefficients)
```

Bootstrap confidence intervals
```{r}
set.seed(888)
B <- 1000

coefs_df <- data.frame(foo$coefficients) %>% 
            tibble::rownames_to_column() %>% 
            spread(key = rowname, value = foo.coefficients)

for (i in 1:B) {
  index <- sample(1:nrow(train_v2_imp), nrow(train_v2_imp), replace = TRUE)
  resample <- train_v2_imp[index, ]
  
  mod <- glm(rx_p_high ~., data = resample, family = binomial)
  coefs <- data.frame(mod$coefficients) %>% 
           tibble::rownames_to_column() %>% 
           spread(key = rowname, value = mod.coefficients)
  
         
         coefs_df <- bind_rows(coefs_df, coefs)
}

summary(coefs_df)
```







The rest isn't organized well because I was just trying out different stuff






```{r}
train_p %>% select(1:20) %>% head(100)
```

```{r}
age_sex_k %>% head()
```

```{r}
write.csv(train_p %>% select(1, 6:20, 50:70, 300:310, 257:267), paste0(scratch, "train_p.csv"))
write.csv(train_impd %>% select(1, 6:20, 50:70, 300:310, 257:267), paste0(scratch, "train_impd.csv"))

```

```{r}
scratch <- "C:/Users/tlang/Documents/GitHub/Summer_Practicum_19_blue_9/scratch/"
```

```{r}
education_attainment %>% select(HC02_EST_VC71, Zip) %>% filter(Zip == 28040


)
```

```{r}
all_na_rows <- all_obs %>% 
  mutate(row_na = rowSums(is.na(all_obs)))  %>% 
  filter(row_na > .18*ncol(all_obs)) 

all_na_rows_zips <- all_na_rows %>% pull(Zip)


all_na_rows %>% select(row_na)


```

```{r}
foo_all <- bind_rows(train_v1, test_v1)

foo_train <- foo_all %>% filter(!(Zip %in% all_na_rows_zips)) %>%
  select(-Zip)


head(foo_train)
dim(foo_train)

```

```{r}
vif_func<-function(in_frame,thresh=10,trace=T,...){

  library(fmsb)
  
  if(any(!'data.frame' %in% class(in_frame))) in_frame<-data.frame(in_frame)
  
  #get initial vif value for all comparisons of variables
  vif_init<-NULL
  var_names <- names(in_frame)
  for(val in var_names){
      regressors <- var_names[-which(var_names == val)]
      form <- paste(regressors, collapse = '+')
      form_in <- formula(paste(val, '~', form))
      vif_init<-rbind(vif_init, c(val, VIF(lm(form_in, data = in_frame, ...))))
      }
  vif_max<-max(as.numeric(vif_init[,2]), na.rm = TRUE)

  if(vif_max < thresh){
    if(trace==T){ #print output of each iteration
        prmatrix(vif_init,collab=c('var','vif'),rowlab=rep('',nrow(vif_init)),quote=F)
        cat('\n')
        cat(paste('All variables have VIF < ', thresh,', max VIF ',
                  round(vif_max,2), sep=''),'\n\n')
        }
    return(var_names)
    }
  else{

    in_dat<-in_frame

    #backwards selection of explanatory variables, stops when all VIF values are below 'thresh'
    while(vif_max >= thresh){
      
      vif_vals<-NULL
      var_names <- names(in_dat)
        
      for(val in var_names){
        regressors <- var_names[-which(var_names == val)]
        form <- paste(regressors, collapse = '+')
        form_in <- formula(paste(val, '~', form))
        vif_add<-VIF(lm(form_in, data = in_dat, ...))
        vif_vals<-rbind(vif_vals,c(val,vif_add))
        }
      max_row<-which(vif_vals[,2] == max(as.numeric(vif_vals[,2]), na.rm = TRUE))[1]

      vif_max<-as.numeric(vif_vals[max_row,2])

      if(vif_max<thresh) break
      
      if(trace==T){ #print output of each iteration
        prmatrix(vif_vals,collab=c('var','vif'),rowlab=rep('',nrow(vif_vals)),quote=F)
        cat('\n')
        cat('removed: ',vif_vals[max_row,1],vif_max,'\n\n')
        flush.console()
        }

      in_dat<-in_dat[,!names(in_dat) %in% vif_vals[max_row,1]]

      }

    return(names(in_dat))
    
    }
  
  }
```

VIF stepwise selection
```{r}
foo_vif <- vif_func(foo_train %>% dplyr::select(-t_rx_p), thresh = 5, trace = T)
saveRDS(foo_vif, paste0(scratch,"VIF_5_col5_row18_notest.rds"))
vif_5_train <- foo_train[c("t_rx_p", foo_vif)]

dim(vif_5_train)
head(vif_5_train)
```


stepwise 
```{r}
lm <- lm(t_rx_p ~., data = vif_5_train)
step <- stepAIC(lm, direction = "both")

step_var <- step$coefficients %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  filter(rowname != "(Intercept)") %>%
  pull(rowname)

step

step_train <- vif_5_train[c("t_rx_p", step_var)]

lm_step <- train(t_rx_p ~., data = step_train, method = "lm")

rf_step <- train(t_rx_p ~., data = step_train, method = "ranger")

saveRDS(step_train, paste0(data,"step_train.rds"))
```



```{r}
set.seed(888)
boruta_train_foo <- Boruta(rx_p_high ~., data = foo_train, doTrace = 2, maxRuns = 88)

final_boruta_foo <- TentativeRoughFix(boruta_train_foo)

boruta_df_foo <- attStats(final_boruta_foo) %>% 
  tibble::rownames_to_column() %>% arrange(desc(meanImp))

imp_p_foo <- getSelectedAttributes(final_boruta_foo, withTentative = T)
```

```{r}
foo_train <- foo_train[c('rx_p_high', imp_p_foo)]

rf_v1_foo <- train(rx_p_high ~., data = foo_train, method = "ranger")

rf_v1_foo

table(foo_train$rx_p_high) / nrow(foo_train)
```

```{r}
boruta_df_type <-  boruta_df %>% mutate(enroll = str_detect(boruta_df$rowname, "enroll"),
                     poverty = str_detect(boruta_df$rowname, "poverty"),
                     income = str_detect(boruta_df$rowname, "income"),
                     employement =  str_detect(boruta_df$rowname, "emply"), 
                     age_sex =  str_detect(boruta_df$rowname, "age_sex"),
                     martial =  str_detect(boruta_df$rowname, "martial"),
                     education =  str_detect(boruta_df$rowname, "edu"))

write.csv(boruta_df_type, paste0(scratch, "boruta_df_REGRESSION_w_type.csv"))
```










Scratch
They are percentages
```{r}
names(dem_c)

age_sex_k

foo <- age_sex %>% select(5:56) %>% 
  select(starts_with("HC01")) %>%
  mutate_all(funs(as.double(.)))

foo$total <- rowSums(foo)

foo$total
```




