---
title: "Exploration"
author: "Tommy Lang"
date: "7/3/2018"
output:
  html_notebook:
    code_folding: hide
    df_print: paged
    fig_height: 4
    fig_width: 7
    highlight: tango
    number_sections: yes
    theme: readable
    toc: yes
    toc_float: yes
---

# Packages, Data and Custom Functions

Custom Functions:
This code chunk contains custom fucntions that I use to help automate or make
tasks easier.
```{r message=FALSE}
LoadPackages <- function(packages) {
  # Load or install packages if they aren't already loaded.
  #
  # Args:
  #   packages: a vector of package names
  #
  for (package in packages) {
    if (!require(package, character.only=T, quietly=T)) {
      if (!package %in% installed.packages()) install.packages(package)
      library(package, character.only=T)
    }
  }
}

ColNa <- function(df) {
  # Return a vector of column names that have NA values
  #
  # Args:
  # df: data frame 
  #
  # Returns:
  #  vector of column names that have NAs 
  df <- tbl_df(df)
  v <- c()
  j <- 1
  for(i in 1:ncol(df)) {
    x <- df[ ,i]
    xRmvNA <- x[!is.na(x),]
    lenx <- nrow(x)
    lenxRmvNA <- nrow(xRmvNA)
    if(lenx != lenxRmvNA ) {
      v[j] <- colnames(df[ ,i])
      j <- j+1
    }
  }
  return(v)
}
```

Load Packages:
Packages contain functions that others write that help with doing stuff
```{r, results=FALSE}
# I use my custom function LoadPackages to load or install packages
LoadPackages(c("dplyr", "haven", "stringr", "tidyr", "ggplot2"))
```


Read in data
```{r results = FALSE}
data_path <- 'E:/Tommy/Original_Data/Data'
# The list.files function gets the file names in a specified directory
# file_names contains the file names of all the data sets
file_names <- list.files(path = data_path, recursive = TRUE)

# Initialize a vector to hold data frame names
df_names <- c()
i <- 1

# This loop goes through the file names and reads it into R
for(name in file_names) {
  # create variable name for df
  df_name <- str_replace_all(name, " |_with_ann2|.sas7bdat|/acs_16_5yr|_records", "")
  # read in data
  df <- read_sas(paste0(data_path, "/", name))
  df <- df %>% mutate_all(funs(as.character(.)))
  # attach df to variable name
  assign(df_name, df) 
  print(paste0("done with: ", df_name, " ", i,"/",length(file_names)))
  i <- i+1
  # add the current iteration of the data frame name to the df_names vector
  df_names <- c(df_names, df_name)
}
```

# Data Descritpions

DF names for the data that was read in.  
- There are 27 sets of demographics data. 9 simliar sets for each state (MA NC OR)  
- The data sets that start with copy are exact copies of other datasets and can be ignored  
- The medication_details dataset has some info about the drug (ex. price, manufacture etc.)  
- rx_nqty: quantity of NEW opiod pills for each month by zip code  
- rx_nrx: number of NEW opiod prescriptions for each month by zip code  
- rx_tqty: quantity of TOTAL opiod pills for each month by zip code  
- rx_trx: number of TOTAL opiod prescriptions for each month by zip code  
```{r}
df_names %>% as.data.frame()
```
  
The medication_details dataset has some info about the drug (ex. price, manufacture etc.)
```{r}
medication_details
```
  
rx_nqty: quantity of NEW opiod pills for each month by zip code
```{r}
rx_nqty
```
  
rx_nrx: number of NEW opiod prescriptions for each month by zip code
```{r}
rx_nrx
```
  
rx_tqty: quantity of TOTAL opiod pills for each month by zip code
```{r}
rx_tqty
```
  
rx_trx: number of TOTAL opiod prescriptions for each month by zip code
```{r}
rx_trx
```
  
MA_s0101: Age and sex demographics data for each zip code in massachusetts  
Column HC01_EST_VC01: is total population for the respective zip code  
Column HC02_EST_VC01: total male population for the respective zip code  
Column HC03_EST_VC01: total femal population for respective zip code  
- You can view the data dictionary to find out what the other columns mean  
- The other demographics data sets likely have a very simialr format  
```{r}
MA_s0101
```

  
Check that the files named with copy really just are duplicates  
```{r, results=FALSE}
rx_nqty %>%
  all_equal(Copyofrx_nqty)
Copyofrx_nrx %>%
  all_equal(rx_nrx)
Copyofrx_tqty %>%
  all_equal(Copyofrx_tqty)
Copyofrx_trx %>%
  all_equal(rx_trx)
```

# Total Rx By State

Prepare data to see total rx by state for each month
```{r}
rx_trx_t <- rx_trx %>% select(ST, starts_with("TRx"))

rx_trx_t <- rx_trx %>%
  select(ST, starts_with("TRx")) %>%
  group_by(ST) %>% 
  summarise_all(funs(sum(.))) %>% 
  ungroup() %>% 
  gather(key = "date", value = TRx, -ST) %>%
  mutate(date = str_replace_all(date, "TRx_", "")) %>% 
  mutate(date = as.Date(date, '%m%d%Y')) %>%
  mutate(pop = ifelse(ST == 'MA', 6.86, 
                      ifelse(ST == "OR", 4.143, 10.27)),
         rx_pop_ratio = TRx / pop)

# prepare data to see difference between total rx for NC and MA
MA_rx_pop <- rx_trx_t %>% 
  filter(ST == "MA") %>% 
  mutate(MA_rx = rx_pop_ratio) %>% 
  select(MA_rx)

OR_rx_pop <- rx_trx_t %>% 
  filter(ST == "OR") %>% 
  mutate(OR_rx = rx_pop_ratio) %>% 
  select(OR_rx)

NC_rx_pop <- rx_trx_t %>% 
  filter(ST == "NC") %>% 
  mutate(NC_rx = rx_pop_ratio) %>% 
  select(NC_rx)

diff_df <- bind_cols(rx_trx_t %>% distinct(date), MA_rx_pop, OR_rx_pop, NC_rx_pop) %>%
  mutate(NC_MA_diff = NC_rx - MA_rx)

```

Line plot of total rx by state for each month
```{r}
ggplot(data = rx_trx_t, aes(x = date, y = TRx, color = ST)) +
  geom_line() +
  ggtitle("Total Rx")

ggplot(data = rx_trx_t, aes(x = date, y = rx_pop_ratio, color = ST)) +
  geom_line() +
  ggtitle("Total Rx per Million Residents")

ggplot(data = diff_df, aes(x = date, y = NC_MA_diff)) +
  geom_line() +
  ggtitle("Diff Total Rx per Million Residents Between NC and MA")
```
  
  
Bar Chart of Total Scripts for each State
```{r}

ggplot(data = rx_trx_t %>% filter(date == '2017-08-31'), aes(x = ST, y = rx_pop_ratio)) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  ggtitle("Total Scripts Per Mil Residents in August")
```


# MISC (scratch / junk).


```{r}
foo <- rx_trx %>% group_by(city, ST, Zip) %>% summarise(sum(TRx_08312017))
```

```{r}
# cast to numeric data type
MA_s0101_d <- MA_s0101 %>% mutate_all(funs(as.double(.)))

# get col names that have NA values
na <- ColNa(MA_s0101_d)

# get all col names
all <- names(MA_s0101)

# this  is column names that don't have any NA values
setdiff(all,na)
```


Write datesets out as csv files
```{r}
for (name in df_names) {
  write.csv(get(name), paste0('E:/Tommy/scratch/csv/',name,".csv"))
}

```


Replace non numeric values with empty string
```{r}
income <- bind_rows(MA_s1901, NC_s1901, OR_s1901)

income_keep <- income %>% 
  select(Zip, contains("VC01"), contains("VC13"), contains( "VC15"))

str_replace_all("2,5a60.03.2.-", "[^.0-9]+", "")


ReplaceNonNum <- function(x) {
  str_replace_all(x, "[^.0-9]+", "")
}

income_keep_c <- income_keep %>% mutate_all(funs(ReplaceNonNum))
income_keep_c[income_keep_c == ""] <- NA
```

Summarize the data
```{r}
income_keep_c %>% mutate_all(funs(as.double(.))) %>% summary()
```

 Check the missing values are truly missing
```{r}
col_names <- names(income_keep)

missing_values <- c()
foo <- c()

for(name in col_names) {
  mis_zip <- income_keep_c %>% 
    filter(is.na(get(name))) %>% pull(Zip)
  
  org_missing <- income_keep %>% filter(Zip %in% as.character(mis_zip))
  foo <- org_missing %>% pull(get(name))
  missing_values <- c(missing_values, foo)
}

table(missing_values)
74+105+118+199+46+61+1776+103
length(missing_values)

col <- 'HC04_EST_VC15'

mis_zip <- income_keep_c %>% filter(is.na(get(col))) %>% pull(Zip)

foo <- income_keep %>% filter(Zip %in% as.character(mis_zip))

table(foo %>% pull(get(col)))
```

